taxize - taxonomic search and retrieval in R

### 2013-05-28 inst/doc/taxize_withcode.Rnw

% \usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
% \usepackage[english]{babel}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\author{Eduard Sz\"{o}cs}
\email[E-mail: ]{szoe8822@uni-landau.de}
\affiliation{Institute for Environmental Sciences, University Koblenz-Landau, Fortstraße 7, 76829 Landau, Germany}
\keywords{taxonomy; R; software; data; API}

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{webb2002phylogenies}, ecological networks \cite{REF}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example:

\begin{figure}[!h] 
\centering 
<<phylomaticphylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE>>=
# Input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

# Plot the tree
plot(tree, cex=1)
@
\caption{A Phylogeny for the three species.} 
\end{figure}

@@

>>>>

% \usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
\usepackage{float}
% \usepackage[english]{babel}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\author{Eduard Sz\"{o}cs}
\email[E-mail: ]{szoe8822@uni-landau.de}
\affiliation{Institute for Environmental Sciences, University Koblenz-Landau, Fortstr. 7, 76829 Landau, Germany}
\keywords{taxonomy; R; software; data; API}

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{webb2002phylogenies}, ecological networks \cite{rafferty2013phylogenetic}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example, producing the tree in figure \ref{fig:phylomatic}:

\begin{figure}[H] 
\centering 
<<phylomaticphylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE>>=
# Input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

# Plot the tree
plot(tree, cex=1)
@
\caption{A Phylogeny for the three species.} 
\label{fig:phylomatic}
\end{figure}

@@

\subsection{Matching species tables with different taxonomic resolution}

### 2013-05-28 inst/doc/taxize_withcode.tex

% \usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
% \usepackage[english]{babel}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{webb2002phylogenies}, ecological networks \cite{REF}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example:

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Input the taxonomic names}
taxa <- \hlfunctioncall{c}(\hlstring{"Poa annua"}, \hlstring{"Abies procera"}, \hlstring{"Helianthus annuus"})

@@

\caption{A Phylogeny for the three species.} 
\end{figure}

>>>>

% \usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
\usepackage{float}
% \usepackage[english]{babel}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

Ecologists are increasingly taking a phylogenetic approach to ecology, applying phylogenies to topics such as the study of community structure \cite{webb2002phylogenies}, ecological networks \cite{rafferty2013phylogenetic}, functional trait ecology \cite{REF}. Yet, Many biologists are not adequately trained in reconstructing phylogenies. Fortunately, there are some sources for getting a phylogeny without having to know how to build one; one of these is for angiosperms, called Phylomatic \cite{webb2005}. We have created a workflow in taxize that accepts a species list, and taxize works behind the scenes to get higher taxonomic names, which are required by Phylomatic to get a phylogeny. Here is a short example, producing the tree in figure \ref{fig:phylomatic}:

\begin{figure}[H] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Input the taxonomic names}
taxa <- \hlfunctioncall{c}(\hlstring{"Poa annua"}, \hlstring{"Abies procera"}, \hlstring{"Helianthus annuus"})

@@

\caption{A Phylogeny for the three species.} 
\label{fig:phylomatic}
\end{figure}
